Bayesian exponential random graph modelling of KWL Burial network

### 2020-04-04 analysis/paper/paper.Rmd
add sentences about goodness-of-fit

The computational processes in this paper were performed by the ergm package for simulation and model specification and then bergm package using R programming [@Hunter2008; @Morris2008; @Caimo2014]. We set the number of chains to eight. For each chain, the number of burn-in iterations is 200 and the number of iterations after the burn-in is 2000. We set the number of iterations used to simulate a network y′ at each iteration to 10000.

@@

>>>>

The computational processes in this paper were performed by the ergm package for simulation and model specification and then bergm package using R programming [@Hunter2008; @Morris2008; @Caimo2014]. We set the number of chains to eight. For each chain, the number of burn-in iterations is 200 and the number of iterations after the burn-in is 2000. We set the number of iterations used to simulate a network y′ at each iteration to 10000. The models are assessed by goodness-of-fit (GOF) diagnostics in the Bayesian framework, where the observed network is compared with a set of networks simulated from the estimated posterior distribution of the parameters of the model [@Caimo2011; @Caimo2017]. This provides a statistical way to check how well the estimated posterior parameter distribution can reproduce networks similar to the general structural features of the observed network.

@@

Figure shows the Bayesian goodness of fit diagnostics plots where the red lines represent the distributions of the observed data and the box plots represent the GOF distributions of 10000 network graphs simulated from ERGMs based on the estimated posterior distribution. The grey lines mark the 95% intervals.
